### 2023-07-10 tesis_Ashish/Chapter5/chapter5.tex
AS thesis update
update

\chapter{Systematic uncertainty in PCC luminosity measurement}  %Title of the First Chapter

@@

@@

>>>>

\chapter{Run 3 Luminosity Measurement}  %Title of the First Chapter

@@

%Please ask Luis for latest 2022 calibration plots

%module veto plots are in slides from Antonio in December PCC meeting

%Afterglow residuals are in my slides in PCC meeting  January , February

%Chapter 5: Run 3 Luminosity Measurement

%Detector Module selection
%Afterglow Model- Detector Module selection
%vdM Calibration Results
%Luminosity for Physics Fills
%Systematic Uncertainties

\section{Detector Module selection}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_dataset.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
   2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_periodC_first_iteration}
\caption[2018 CMS luminosity data taking periods.]{%
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_periodC_final_iteration.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_per_period_veto.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                         
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_common_veto.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\section{Afterglow Model}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_type1res.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_type2res.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\section{vdM Calibration Results}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM_fit.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM_fit_quality-png.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_capsigma.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_peak.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_sigma_vis_per_scan.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                              
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

Sigma Vis =  4.1694 +- 0.002 (stat) Barns
0.06\% statistical error

\section{Luminosity for Physics Fills}

\section{Systematic uncertainties}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_SS_scan.png}
\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
}
\label{fig:period_bound}
\end{figure}

\begin{table}[h]
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{SS1   SS1_avg= 0.76804 +- 0.002478}
        \begin{tabular}{ccc}
        \textbf{BCID} & \textbf{Mean} & \textbf{SEM} \\ 
        \hline
        282 & .7734 & .00570 \\ 
        822 & .7756 & .00578 \\ 
        2944 & .7703 & .00599 \\ 
        3123 & .7478 & .00505 \\ 
        3302 & .7731 & .00521 \\ 
        \end{tabular}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \caption{SS2.  SS2_avg= 0.72026 -+0.002888}
        \begin{tabular}{ccc}
        \textbf{BCID} & \textbf{Mean} & \textbf{SEM} \\ 
        \hline
        282 & .7207 & .00521 \\ 
        822 & .7247 & .00898 \\ 
        2944 & .7306 & .00616 \\ 
        3123 & .7038 & .00563 \\ 
        3302 & .7215 & .00560 \\ 
        \end{tabular}
    \end{minipage}
\end{table}

SS bkg= 0.74415 +- 0.002683

\begin{comment}

@@

\end{comment}

### 2023-07-10 tesis_Ashish/Chapter6/chapter6.tex
AS thesis update
update

@@

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/raw_corr_hist.png}
\caption{%
   Raw and corrected PCC with its ratio.
}
\label{fig:stability_D4}
\end{figure}

@@

\begin{comment}

\begin{figure}[!htp]
\centering
\includegraphics[width=|\textwidth]{ashish_thesis/new_framework_vdm.png}
\caption{%
   klm
}
\label{fig:vdm_new_f}
\end{figure}

@@

@@

\begin{table}[!ht]
\centering
\topcaption{%
    pcc visible cross section for different module vetolist.
}
\begin{tabular}{ccccc}
    \textbf{Module veto list} & \textbf{PCC visible cross section values (mb)} & \textbf{Uncertainty} \\ \hline
    Old veto (LUM PAS 2018) & 5982 & 37 (0.08%) stat+syst \\
    New per period veto (Period B) & 9229.4  & 7.7 (0.08%) stat \\
    4\% rms common veto & 1673.49  & 0.93 (0.05%) stat \\
    2\% rms common veto & 959.94  & 0.92 (0.09%) stst \\
\end{tabular}
\label{tab:pccvis_diffveto}
\end{table}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/stability_unc_diff_veto.png}
\caption{%
kjbhgjklh
}
\label{fig:stabilityuncallveto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_linearity_sys_unc.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_new_veto_linearity.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_linearity_sys_unc_2per_common_veto.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/lineairty_diff_veto_sys_unc.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_stability_4_commonveto.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/lineairty_diff_veto_period_variation_slope.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type1_type2_af_residuals_oldveto_oldp.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\end{comment}

>>>>

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
\caption{%                                                                                                                                                                                                            
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_begin}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
\caption{%                                                                                                                                                                                                            
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_L0_veto}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/raw_corr_hist.png}
\caption{%
   Raw and corrected PCC with its ratio.
}
\label{fig:stability_D5}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/veto_change_same_af.png}
\caption{%                                                                                                                                                                                                            
    ratio of scale factor for new and old veto.
}
\label{fig:af_change_veto}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/new_framework_vdm.png}
\caption{%
   klm
}
\label{fig:vdm_new_f}
\end{figure}

@@

%\begin{comment}

@@

\begin{table}[!ht]
\centering
\topcaption{%
    pcc visible cross section for different module vetolist.
}
\begin{tabular}{ccccc}
    \textbf{Module veto list} & \textbf{PCC visible cross section values (mb)} & \textbf{Uncertainty} \\ \hline
    Old veto (LUM PAS 2018) & 5982 & 37 (0.08\%) stat+syst \\
    New per period veto (Period B) & 9229.4  & 7.7 (0.08\%) stat \\
    4\% rms common veto & 1673.49  & 0.93 (0.05\%) stat \\
    2\% rms common veto & 959.94  & 0.92 (0.09\%) stst \\
\end{tabular}
\label{tab:pccvis_diffveto}
\end{table}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/stability_unc_diff_veto.png}
\caption{%
stability uncertainty all vetoes
}
\label{fig:stabilityuncallveto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_linearity_sys_unc.png}
\caption{%
linearity systematic uncertainty
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_new_veto_linearity.png}
\caption{%
old new veto linearity
}
\label{fig:pcc_hf_new_lin}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_linearity_sys_unc_2per_common_veto.png}
\caption{%
linearity 2 percent veto
}
\label{fig:linearity2perveto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/lineairty_diff_veto_sys_unc.png}
\caption{%
all veto linearity sys uncertainty
}
\label{fig:linearitysys}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_stability_4_commonveto.png}
\caption{%
4 percent veto
}
\label{fig:4perdisklayerstab}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
\caption{%
pcc layer disk mean rms
}
\label{fig:pixellalyerdiskmeanrms}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/lineairty_diff_veto_period_variation_slope.png}
\caption{%
linearity all period
}
\label{fig:linearityperperiod}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type1_type2_af_residuals_oldveto_oldp.png}
\caption{%
residuals af
}
\label{fig:afres}
\end{figure}

%\end{comment}
